---
title: "RRproject-original"
author: "Hanwenmiao436819"
date: "2024-06-08"
output: html_notebook
---

##### Project Translation

# The original project's URL is: https://www.kaggle.com/code/artemburenok/stock-analysis-monte-carlo-build-portfolio

# Author: ARTEM BURENOK

#### Purpose of Analysis:

# - Build moving averages of various stocks
# - Determine correlations between stock returns
# - Create an optimal portfolio
# - Try to predict the future behavior of the stocks

### Code Reproduction Explanation

# I have converted the original project's Python code to R code. Due to Twitter's delisting, 
# there is no stock price information for Twitter on Yahoo Finance. 
# Therefore, the new investment portfolio consists of three companies, 
# which may slightly affect the results.

```{r,eval = FALSE}
# Setting working path
setwd("C:/Users/lulut/Desktop/RRproject436819")
today <- as.Date("2022-02-23")
year_ago <- as.Date(today - 365)
# Three company for data extraction
company_list <- c("TSLA", "MSFT", "AMZN")

library(quantmod)
for (company in company_list) {
  assign(company, getSymbols(company, src = 'yahoo', from = year_ago, to = today, auto.assign = FALSE))
}
save.image(file = "Data.RData")
library(dplyr)
library(corrplot)
library(ggplot2)
library(GGally)
library(xts)
library(MASS)
library(gridExtra)
```

```{r}
rm(list = ls())
load("Data.RData")

for(i in 1:20){
  print(head(eval(parse(text =company_list[i])), 5))
}
```
```{r}
for(i in 1:3){
  temp <- eval(parse(text =company_list[i]))
  colnames(temp) = c("Open","High","Low","Close","Volume","Adjusted")
  assign(company_list[i],temp)
}
rm(temp)
```

```{r,include=FALSE}
Sys.setlocale ("LC_TIME", "English")

```
```{r}
for(i in 1:length(company_list)){
  print(plot(eval(parse(text =company_list[i]))$Adjusted, main = paste0(company_list[i]," Adjusted Close Price"), ylab = "Price", xlab = "Date", type = "l", col = "blue"))
}
```
##Moving average¶
Moving average - function whose value at each point is equal to some average value of the original function for the previous period.

Formula for calculations:

SUM = sum of prices for past x days; MA = SUM / x
```{r}
MA_days <- c(10, 20, 30)
 
for(i in 1:3){
  temp = eval(parse(text =company_list[i]))
  temp$`MA10` <- rollmean(temp$Adjusted, k = 10, fill = NA,align = "right")
  temp$`MA20` <- rollmean(temp$Adjusted, k = 20, fill = NA,align = "right")
  temp$`MA30` <- rollmean(temp$Adjusted, k = 30, fill = NA,align = "right")
  assign(company_list[i],temp)
}
rm(temp)

for(i in 1:20){
  print(head(eval(parse(text =company_list[i])), 5))
}
```
```{r}
plot_graphic <- function(company, company_string) {
  plot(company[,6:9], type = "l", xlab = "Date", ylab = "Price", main = company_string,col = 1:4,legend.loc = "topleft")
}



for (i in 1:length(company_list)) {   
  print(plot_graphic(eval(parse(text =company_list[i])), company_list[i]))
}
```

```{r}
for (i in 1:length(company_list)){
  temp = eval(parse(text =company_list[i]))
  temp$`Daily Returns` <- diff(temp$Adjusted)/stats::lag(temp$Adjusted, k = 1)
  assign(company_list[i],temp)
  hist(na.omit(temp$`Daily Returns`), breaks=50, col='dodgerblue', main=company_list[i], xlab='Daily Returns', ylab='Count',ylim = c(0,40))
  lines(density(na.omit(temp$`Daily Returns`)),col = "blue",lwd = 2)
}

```
```{r}
# Create dataframe with stock returns

stock_returns <- list()
for(i in 1:3){
  stock_returns[[i]] <- eval(parse(text =company_list[i]))$`Daily Returns`
}
stock_returns <- do.call(cbind,stock_returns)
colnames(stock_returns) <- company_list
head(stock_returns)
```

```{r,fig.height=8,fig.width=8}
# Plot pairplot
stock_returns <- na.omit(stock_returns)
ggpairs(stock_returns, 
        upper = list(continuous = wrap("cor", size = 3)), 
        lower = list(continuous = wrap("points", size = 0.5)),
        diag = list(continuous = wrap("barDiag", bins = 30, fill = "blue")))
```

```{r,fig.height=8,fig.width=8}
# Calculate the correlation matrix
corr = cor(stock_returns,use = "complete.obs")
  
# Create the correlogram
corrplot(corr, type = "lower", 
         method = "shade", 
         addCoef.col = "black", 
         tl.col = "black", tl.srt = 45)

```
## Amazon and Microsoft have the most correlated daily profits
```{r}

# Function to create plots
create_plot <- function(data, x_label, y_label) {
  ggplot(data = data, aes(x = x, y = y)) +
    geom_point(alpha = 0.6) +
    geom_smooth(method = "lm", se = FALSE, color = "blue") +
    labs(x = x_label, y = y_label) +
    theme_minimal()
}

# Create plots
k <- 3  
plots <- list()
stock_return <- as.data.frame(na.omit(stock_returns))

# Loop through each combination of stocks
for (i in 1:k) {
  for (j in 1:k) {
    # Plot histogram and density on diagonal
    if (i == j) {
      data <- data.frame(returns = stock_return[, i])
      plots[[length(plots) + 1]] <- ggplot(data, aes(x = returns)) +
        geom_histogram(bins = 40, fill = "lightblue", color = "black") +
        geom_density(alpha = 0.5, color = "red") +
        labs(title = colnames(stock_return)[i], x = "Returns", y = "Frequency") +
        theme_minimal()
    }
    # Plot scatter plot with regression line on lower triangle
    if (i > j) {
      data <- data.frame(x = stock_return[, j], y = stock_return[, i])
      plots[[length(plots) + 1]] <- create_plot(data, colnames(stock_return)[j], colnames(stock_returns)[i])
    }
    # Plot contour plot on upper triangle
    if (i < j) {
      data <- data.frame(x = stock_return[, j], y = stock_return[, i])
      plots[[length(plots) + 1]] <- ggplot(data, aes(x = x, y = y)) +
        geom_density_2d() +
        labs(title = paste(colnames(stock_returns)[i], "vs", colnames(stock_returns)[j]), x = colnames(stock_returns)[j], y = colnames(stock_returns)[i]) +
        theme_minimal()
    }
  }
}

# Arrange plots in a grid with larger plots
grid.arrange(grobs = plots, ncol = k, nrow = k, top = "Stock Returns Pair Plot")

```

##Portfolio strategy
#Let's try to make an optimal portfolio of four stocks. Following the classical theory, it is necessary to minimize risk and maximize profitability. We will generate random ratios of stocks, calculate the risk and profitability of each portfolio according to the given formulas.

#The expected return of the portfolio is the total expected return of the securities included in it, weighted taking into account their share in the portfolio.

```{r}
# Calculate mean income for each stock
stock_returns <- na.omit(stock_returns)
mean_income <- apply(stock_returns, 2, mean)

# Calculate covariance matrix of returns
cov_returns <- cov(stock_returns)

# Number of stocks
count <- ncol(stock_returns)

# Print mean income and covariance matrix
print(mean_income)
print(cov_returns)
```
```{r}
# Function to generate random portfolio
randomPortfolio <- function(input) {
  set.seed(input)
  share <- exp(rnorm(count))
  share <- share / sum(share)
  return(share)
}

# Function to calculate portfolio income
IncomePortfolio <- function(Rand) {
  return(sum(mean_income * Rand))
}

# Function to calculate portfolio risk
RiskPortfolio <- function(Rand) {
  return(sqrt(t(Rand) %*% cov_returns %*% Rand))
}

combinations <- 4000
risk <- rep(0, combinations)
income <- rep(0, combinations)
portfolio <- matrix(0, nrow = combinations, ncol = count)

# Loop to create new combinations of shares
for (i in 1:combinations) {
  rand <- randomPortfolio(i)
  portfolio[i, ] <- rand
  risk[i] <- RiskPortfolio(rand)
  income[i] <- IncomePortfolio(rand)
}

```

```{r}

# Convert numpy arrays to R vectors/matrices
risk <- risk * 100
income <- income * 100

# Find index of maximum Sharpe ratio
MaxSharpRatio <- which.max(income / risk)

# Create scatter plot
scatter_plot <- ggplot() +
  geom_point(data = data.frame(Risk = risk, Income = income), aes(x = Risk, y = Income), color = "blue", shape = 16) +
  geom_point(data = data.frame(Risk = risk[MaxSharpRatio], Income = income[MaxSharpRatio]), aes(x = Risk, y = Income), color = "red", shape = 19, size = 3) +
  labs(x = "Risk", y = "Income", title = "Portfolios and max sharpe ratio portfolio") +
  theme_minimal()

# Show the plot
print(scatter_plot)
```

```{r}
best_port <- portfolio[MaxSharpRatio,]
for (i in 1:length(company_list)) {
  print(paste(company_list[i], ": ", best_port[i]))
}
```
##Due to the absence of one stock, the weights are different. However, looking at the results, heavily investing in Microsoft from 2021 to 2022 was the right move. Although Tesla didn't perform well in 2022, its stock rose by 90% in 2023 !

##Try to predict price behavior with method Monte Carlo

```{r}
days <- 365
dt <- 1 / days

mu <- apply(stock_returns, 2, mean)
sigma <- apply(stock_returns, 2, sd)

monte_carlo <- function(start_price, days, mu, sigma) {
  price <- rep(0, days)
  price[1] <- start_price
  
  shock <- rep(0, days)
  drift <- rep(0, days)
  
  for (x in 2:days) {
    shock[x] <- rnorm(1, mean = mu * dt, sd = sigma * sqrt(dt))
    drift[x] <- mu * dt
    
    price[x] <- price[x - 1] + (price[x - 1] * (drift[x] + shock[x]))
  }
  
  return(price)
}

sim <- rep(0, 1000)


for(j in 1:3){
  start_price <- tail(eval(parse(text =company_list[j]))$Adjusted,1)
  result <- monte_carlo(start_price, days, mu[company_list[j]], sigma[company_list[j]])
  sim[1] <- result[days]
  plot(result, type = "l", xlab = "Days", ylab = "Price", col = 1,main = paste0("Monte Carlo analysis for ", company_list[j]),ylim = c(0.88*start_price,1.12*start_price))
  for (i in 2:1000) {
  result <- monte_carlo(start_price, days, mu[company_list[j]], sigma[company_list[j]])
  sim[i] <- result[days]
  lines(result, col = i)
  }
  hist(sim, breaks = 100, main = "Histogram of Monte Carlo Simulations", xlab = "Price")
  text(0.6, 0.7, paste("Mean: ", mean(sim), "\nStd: ", sd(sim), "\nStart Price: ", start_price))
}


```
